The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-06 paper.tex
update

  pyFC randomly generates dimensionless 3D scalar field $f(\bold{x})$\ % that is clumpy and porous.
  that obeys the log-normal probability distribution\
  with mean $\mu$ and dispersion $\sigma$,\
  and follows the power-law Kolmogorov spectrum
  \begin{equation}
    D(\bold{k})=\int k^{2} \hat{f}(\bold{k})\hat{f}^{*}(\bold{k})d\Omega \propto k^{-\beta},
    \label{Kolmogorov-spectrum}
  \end{equation}
  where $\hat{f}(\bold{k})$ is the Fourier transform of $f(\bold{x})$.\
  The spectrum $D(\bold{k})$ in the Fourier space is characterized by the power law index $\beta=5/3$,\
  the Nyquist limit $k_{\text{max}}$, and the lower cutoff wave number $k_{\text{min}}$.
  $k_{\text{max}}$ is one-half of the spatial resolution within disc,\
  and $k_{\text{min}}$ is 375.0, corresponding to the maximum size of an individual clump $\sim 20$ pc.\
  \citet{LA2002} and \citet{Wagner2012} have outlined a detailed procedure\
  for constructing a clumpy scalar field, and we do not repeat here.

@@

\subsection{Gamma-ray and microwave emission}
  In this section, we compare the simulated gamma-ray and microwave\
  spectra based on the leptonic AGN jet model with the\
  observed spectra of the Fermi bubbles and the microwave haze.

@@

In the leptonic scenario, the gamma-rays originate from IC scattering of the ISRF by CRe.\
The CRe spectrum follows a power law distribution\
with a spectral index $p=2.4$ and ranges from\
$m_{\text{e}}c^2$ ($0.5$ MeV) to $1.1\times10^{6}m_{\text{e}}c^2$ ($550$ GeV).\

The emissivity of the upscattered photons at the energy $\epsilon_{1}$ is given by\
the double integrals \citep{BLUMENTHAL1970}\
over the range of incident photon energy and the CRe Lorentz factor:

@@

where $\sigma_{T}$ is the Thomson cross section, $c$ speed of light,\
$n(\epsilon)$ the photon number density of ISRF per energy, $\gamma$ the Lorentz factor of CRe,\
$\mathbb{C}$ and $p$ are the normalization constant and spectral index of CRe power-law spectrum.
$\gamma_{\text{min}}(\epsilon)$ is the minimum required Lorentz factor of CRe such that CRe is energetic sufficient for\
producing scattered photon at the energy $\epsilon_{1}$ from an incident photon energy $\epsilon$.\
$\gamma_{\text{max}}$ is the maximum CRe Lorentz factor in the spectrum, i.e. $\gamma_{\text{max}}=10^{6}$.

We integrate the incident photon energy from\
$\epsilon_{\text{min}}=1.13\times10^{-4}$ eV (CMB radiation) to\
$\epsilon_{\text{max}}=13.59$ eV (optical starlight) in order to\
facilitate a reliable interpretation of simulated gamma-ray spectrum.

>>>>

  pyFC randomly generates dimensionless 3D scalar field $f(\bold{x})$\ % that is clumpy and porous.
  that obeys the log-normal probability distribution\
  with mean $\mu$ and dispersion $\sigma$,\
  and follows the power-law Kolmogorov spectrum
  \begin{equation}
    D(\bold{k})=\int k^{2} \hat{f}(\bold{k})\hat{f}^{*}(\bold{k})d\Omega \propto k^{-\beta},
    \label{Kolmogorov-spectrum}
  \end{equation}
  where $\hat{f}(\bold{k})$ is the Fourier transform of $f(\bold{x})$.\
  The spectrum $D(\bold{k})$ in the Fourier space is characterized by the power-law index $\beta=5/3$,\
  the Nyquist limit $k_{\text{max}}$, and the lower cutoff wave number $k_{\text{min}}$.
  $k_{\text{max}}$ is one-half of the spatial resolution within disc,\
  and $k_{\text{min}}$ is 375.0, corresponding to the maximum size of an individual clump $\sim 20$ pc.\
  \citet{LA2002} and \citet{Wagner2012} have outlined a detailed procedure\
  for constructing a clumpy scalar field, and we do not repeat here.

@@

\subsection{Gamma-ray and microwave emission}

  In this section, we compare the simulated gamma-ray and microwave\
  spectra based on the leptonic AGN jet model with the\
  observed spectra of the Fermi bubbles and the microwave haze.\
  The gamma-rays originate from the inverse Compton scattering of ISRF by CRe.\
  The CRe spectrum follows a power-law distribution\
  with a spectral index $p=2.4$ and ranges from\
  $m_{\text{e}}c^2$ ($0.5$ MeV) to $1.1\times10^{6}m_{\text{e}}c^2$ ($550$ GeV),\
  where $m_{\text{e}}c^2$ is the rest mass energy of an electron.

@@

  The emissivity of the upscattered photons at the energy $\epsilon_{1}$ is computed for\
  each computational cell in our simulations\
  using the Klein-Nishina IC cross-section \citep{Jones1968,BLUMENTHAL1970}\
  to handle the ultra-relativistic CRe:

@@

where $\sigma_{T}$ is the Thomson cross section, $c$ speed of light,\
$n(\epsilon)$ the energy distribution of the photon number density in ISRF given by \citet{Porter2017},\
$\gamma$ the Lorentz factor of CRe,\
$\mathbb{C}$ and $p$ are the normalization constant and spectral index of CRe power-law spectrum.
$\gamma_{\text{min}}(\epsilon)$ is the minimum Lorentz factor of CRe\
that allows incident photons to scatter from energy $\epsilon$ to $\epsilon_{1}$.
$\gamma_{\text{max}}$ is the maximum CRe Lorentz factor in the spectrum.

We integrate the incident photon energy from\
$\epsilon_{\text{min}}=1.13\times10^{-4}$ eV (cosmic microwave background radiation) to\
$\epsilon_{\text{max}}=13.59$ eV (optical starlight) in order to\
facilitate a reliable interpretation of simulated gamma-ray spectrum.
